---
title: "Demand prediction"
author: "Diego de Lima"
date: "March 28th, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the packages
```{r, message=FALSE, warning=FALSE}
library(data.table)
library(dplyr)
library(stringr)
library(tm)
library(corpus)
library(tidyr)
library(ggplot2)
library(knitr)
```

## Loading the datasets
```{r}
products <- fread('producto_tabla.csv', encoding = 'UTF-8')
clients <- fread('cliente_tabla.csv', encoding = 'UTF-8')
location <- fread('town_state.csv', encoding = 'UTF-8')
train_set <- fread('train_set2.csv', encoding = 'UTF-8')
```
## Preparing the dataset

Preparing products
```{r, results='asis'}
kable(head(products))
kable(tail(products))
```

Removing the first row from products table
```{r}
products <- products[-1,]
```

Function to prepare data frame for products
```{r}
prepare_products <- function(df){
  # Removing the redundancy of the id from the end of the NombreProducto
  df <- df %>% mutate(NombreProducto = gsub('\\d+$', '', NombreProducto))
  
  # Putting the product name into a new variable
  df <- df %>% mutate(Product = gsub('  ', ' ', gsub(' +$', '', str_extract(NombreProducto, '[^\\d]+'))))
  
  # Putting the brand into a new variable and removing its spaces
  df <- df %>%
    mutate(Brand = str_extract(NombreProducto, '\\w+ $'))
  df <- df %>% mutate(Brand = gsub(' ', '', Brand))
  
  # Putting the weight in grams into a new variable
  df <- df %>%
    mutate(
      Weight_grams = str_extract(NombreProducto, '\\d+(?=\\s*g)|\\d+(?=\\s*G)'),
      Weight_kg = str_extract(NombreProducto, '\\d+(?=\\s*Kg)|\\d+(?=\\s*kg)'),
      Weight_grams = if_else(!is.na(Weight_grams), Weight_grams, as.character(as.numeric(Weight_kg) * 1000))
    ) %>%
    select(-Weight_kg)
  
  # Putting the quantities into a new variable
  df <- df %>%
    mutate(
      Quantity = str_extract(NombreProducto, '\\d+(?=\\s*p)'))
  
  # Putting the volumes into a new variable
  df <- df %>%
    mutate(
      Volume = str_extract(NombreProducto, '\\d+(?=\\s*ml)|\\d+(?=\\s* ml)'))
  
  # Removing the stopwords
  df_2 <- df
  df_2 <- df_2 %>% mutate(Product = removeWords(Product, stopwords_es))
  
  # Subsetting the dataset
  df_3 <- df_2[, c(1,3)]
  # Combining into product names
  df<- df_2[-2] %>%
    mutate(
      Product = paste(Product, ' ', Brand, sep = ''),
      Product = if_else(!is.na(Weight_grams), paste(Product,' ', Weight_grams, 'g', sep = ''), Product),
      Product = if_else(!is.na(Quantity), paste(Product,' ', Quantity, 'p', sep = ''), Product),
      Product = if_else(!is.na(Volume), paste(Product,' ', Volume, 'ml', sep = ''), Product)) %>%
    select(Producto_ID, Product)
  
  return(df)
}
```

Calling the function to prepare the products data frame
```{r, results='asis'}
products <- prepare_products(products)
kable(head(products))
```

Updating the train_set
```{r, results='asis'}
train_set <- merge(products, train_set, by = 'Producto_ID')
kable(head(train_set))
```

## Preparing clients
Removing duplicate data
```{r}
clients <- distinct(clients, Cliente_ID, .keep_all = T)
```

Removing excedent spaces
```{r, results='asis'}
clients <- clients %>% mutate(NombreCliente = gsub('  ', '', NombreCliente))
kable(head(clients))
train_set <- merge(clients, train_set, by = 'Cliente_ID')
kable(head(train_set))
```

## Preparing Location
Removing State
```{r, results='asis'}
location <- location[, 1:2]
kable(head(location))
train_set <- merge(location, train_set, by = 'Agencia_ID')
kable(head(train_set))
```

Checking if there are different channels for the same Town
```{r, results='asis'}
kable(head(table(data.frame(Channel_Location = paste(train_set$Town, train_set$Canal_ID))[, 1]), 50), caption = '50 first results')
```

**Since there are different channels for the same Town, there's a possibility of some channel be sending more product than expected.**

Checking the returned units by channel
```{r, results='asis'}
return_by_channel <- distinct(train_set %>% group_by(Canal_ID) %>% mutate(Returns = sum(Dev_uni_proxima)) %>% select(Canal_ID, Returns), Canal_ID, .keep_all = T)
return_by_channel <- data.frame(return_by_channel[order(-return_by_channel$Returns), ])
return_by_channel <- return_by_channel %>% mutate(
  Cum_Return = cumsum(Returns),
  Perc = round((Returns / sum(Returns)) * 100 , 2),
  Cum_Perc = round((Cum_Return / sum(Returns)) * 100 , 2)
)
kable(return_by_channel)
ggplot(return_by_channel,
       aes(x = reorder(Canal_ID, -Returns), y = Returns)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('RETURN BY CHANNEL') +
  xlab('CHANNELS') +
  ylab('RETURN IN UNITS') +
  ylim(0, max(return_by_channel$Returns) * 1.05) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(hjust = 0.5))
```

**As checked on the plot, the channels 1 and 5 have more than 80% of the returns.**
**Since constraints by channel have not been informed, at this point it will be suggested to integrate the total of demand to all channels by sharing the total of sells.**
**So, channel will not be considered in the following analyses.**
**The route will also not be considered, since it's to do to the strategy of transportation.**

Converting train_set into data.frame
```{r, results='asis'}
train_set <- data.frame(train_set)
kable(head(train_set))
```

Checking the variables type
```{r}
str(train_set)
```

**The IDs (Agencia, Cliente and Producto) could be categoric variables. But, to guarantee that possible future data won't be duplicated by using different IDs, it will be considered to use the description for each one:**
**Town for Agencia_ID, NombreCliente for Cliente_ID, Product for Producto_ID.**

## Products Analysis
```{r}
products_analysis <- train_set[,c(6, 10:14)]
products_analysis <- distinct(products_analysis %>%
                                group_by(Product) %>%
                                mutate(
                                  Venta_uni_hoy = sum(Venta_uni_hoy),
                                  Venta_hoy = sum(Venta_hoy),
                                  Dev_uni_proxima = sum(Dev_uni_proxima),
                                  Dev_proxima = sum(Dev_proxima),
                                  Demanda_uni_equil = sum(Demanda_uni_equil)
                                ), Product, .keep_all = T)
```

Checking the number of products
```{r}
length(unique(products_analysis$Product))
```

**Since the number of products reaches to 815, it's considered too much to address throught.**
**So, the Pareto's Theorem will be considered to sub set the products that represent 80% of the total of Demand, Return in units or Return in pesos.**
**To choose the best strategy will be chosen the dataset with the lowest number of products and the highest potential to reduce the number of returns.**

Demand by product
```{r}
demand_by_product <- data.frame(products_analysis[order(-products_analysis$Demanda_uni_equil),][,c(1, 6)])
demand_by_product <- demand_by_product %>% mutate(
  Cum_Demand = cumsum(Demanda_uni_equil),
  Perc = round((Demanda_uni_equil / sum(Demanda_uni_equil)) * 100 , 2),
  Cum_Perc = round((Cum_Demand / sum(Demanda_uni_equil)) * 100 , 2)
)
```

Table of the products which correspond 80% of the total of the demand
```{r, results='asis'}
kable(demand_by_product %>% filter(Cum_Perc <= 80))
```

Return by product
```{r}
return_by_product <- data.frame(products_analysis[order(-products_analysis$Dev_uni_proxima),][,c(1, 4)])
return_by_product <- return_by_product %>% mutate(
  Cum_Dev = cumsum(Dev_uni_proxima),
  Perc = round((Dev_uni_proxima / sum(Dev_uni_proxima)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Dev_uni_proxima)) * 100 , 2)
)
```

Table of the products which correspond 80% of the total of the total of returns in units
```{r, results='asis'}
kable(return_by_product %>% filter(Cum_Perc <= 80))
```

Cost of return by product
```{r}
cost_by_product <- data.frame(products_analysis[order(-products_analysis$Dev_proxima),][,c(1, 5)])
cost_by_product <- cost_by_product %>% mutate(
  Cum_Dev = cumsum(Dev_proxima),
  Perc = round((Dev_proxima / sum(Dev_proxima)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Dev_proxima)) * 100 , 2)
)
```

Table of the products which correpond 80% of the total of the costs with return
```{r, results='asis'}
kable(cost_by_product %>% filter(Cum_Perc <= 80))
```

**Plots of the top 10 Products which correspond 80% of the DEMAND, RETURN (UNITS) and COST WITH RETURN.**
**It's been shown only the top 10 because of the legibility of the plots**

DEMAND
```{r}
ggplot(demand_by_product[1:10, ],
       aes(x = reorder(Product, -Demanda_uni_equil), y = Demanda_uni_equil)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('DEMAND BY PRODUCT (10+)') +
  xlab('PRODUCTS') +
  ylab('DEMAND IN UNITS') +
  ylim(0, max(demand_by_product$Demanda_uni_equil) * 1.05) +
  labs(subtitle = paste(
    round(nrow(demand_by_product %>% filter(Cum_Perc <= 80)) / nrow(demand_by_product) * 100, 2),
    "% of the ",
    nrow(demand_by_product),
    " Products represent ",
    max(demand_by_product %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the Demand",
    'The top 10 represent ',sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(demand_by_product[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 36.71% of the total of the demand*

RETURNED UNITS
```{r}
ggplot(return_by_product[1:10, ],
       aes(x = reorder(Product, -Dev_uni_proxima), y = Dev_uni_proxima)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('PRODUCTS WITH THE HIGHEST RETURNED UNITS (10+)') +
  xlab('PRODUCTS') +
  ylab('RETURNED UNITS') +
  ylim(0, max(return_by_product$Dev_uni_proxima) * 1.05) +
  labs(subtitle = paste(
    round(nrow(return_by_product %>% filter(Cum_Perc <= 80)) / nrow(return_by_product) * 100, 2),
    "% of the ",
    nrow(return_by_product),
    " Products represent ",
    max(return_by_product %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the returned units", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(return_by_product[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 46.82% of the total of the returned units*

COST OF RETURN
```{r}
ggplot(cost_by_product[1:10, ],
       aes(x = reorder(Product, -Dev_proxima), y = Dev_proxima)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('PRODUCT WITH THE HIGHEST COSTS OF RETURNS (10+)') +
  xlab('PRODUCTS') +
  ylab('RETURN IN PESOS') +
  ylim(0, max(cost_by_product$Dev_proxima) * 1.05) +
  labs(subtitle = paste(
    round(nrow(cost_by_product %>% filter(Cum_Perc <= 80)) / nrow(cost_by_product) * 100, 2),
    "% of the ",
    nrow(cost_by_product),
    " Products represent ",
    max(cost_by_product %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the Costs of the Returns", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(cost_by_product[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 24.48% of the total of the costs with returns*

**As seen above, a small parcel of the products represent 80% of de DEMAND, RETURNED UNITS AND COSTS WITH RETURNS.**
**At this point it's being considered to address through the products which represent about 80% of the returned units in a trying to reduce wastes. By focusing on the features with the most returns, it can be reached multiple benefits, for example: costs reduction, better use of transports, improvement on the relationship with clients.**

List of products which represent about 80% of the returns
```{r}
list_products <- as.vector(unlist(return_by_product %>% filter(Cum_Perc <= 80) %>% select(Product)))
```

## Towns Analysis using the list of products which represent 80% of the total of returned units
```{r}
towns_analysis <- train_set %>% filter(Product %in% list_products) %>% select(Town, Venta_uni_hoy, Venta_hoy, Dev_uni_proxima, Dev_proxima, Demanda_uni_equil)
towns_analysis <- distinct(towns_analysis %>%
                                group_by(Town) %>%
                                mutate(
                                  Venta_uni_hoy = sum(Venta_uni_hoy),
                                  Venta_hoy = sum(Venta_hoy),
                                  Dev_uni_proxima = sum(Dev_uni_proxima),
                                  Dev_proxima = sum(Dev_proxima),
                                  Demanda_uni_equil = sum(Demanda_uni_equil)
                                ), Town, .keep_all = T)
```

Checking the number of locations
```{r}
length(unique(towns_analysis$Town))
```

Demand by town
```{r}
demand_by_town <- data.frame(towns_analysis[order(-towns_analysis$Demanda_uni_equil),][,c(1, 6)])
demand_by_town <- demand_by_town %>% mutate(
  Cum_Demand = cumsum(Demanda_uni_equil),
  Perc = round((Demanda_uni_equil / sum(Demanda_uni_equil)) * 100 , 2),
  Cum_Perc = round((Cum_Demand / sum(Demanda_uni_equil)) * 100 , 2)
)
```

Table of the towns which correspond 80% of the total of the demand of the list_products
```{r, results='asis'}
kable(demand_by_town %>% filter(Cum_Perc <= 80))
```

Return by town
```{r}
return_by_town <- data.frame(towns_analysis[order(-towns_analysis$Dev_uni_proxima),][,c(1, 4)])
return_by_town <- return_by_town %>% mutate(
  Cum_Dev = cumsum(Dev_uni_proxima),
  Perc = round((Dev_uni_proxima / sum(Dev_uni_proxima)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Dev_uni_proxima)) * 100 , 2)
)
```

Table of the towns which correspond 80% of the total of returned units of the list_products
```{r, results='asis'}
kable(return_by_town %>% filter(Cum_Perc <= 80))
```

Cost of return by town
```{r}
cost_by_town <- data.frame(towns_analysis[order(-towns_analysis$Dev_proxima),][,c(1, 5)])
cost_by_town <- cost_by_town %>% mutate(
  Cum_Dev = cumsum(Dev_proxima),
  Perc = round((Dev_proxima / sum(Dev_proxima)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Dev_proxima)) * 100 , 2)
)
```

Table of the towns which correspond 80% of the total of the costs with returns of the list_products
```{r, results='asis'}
kable(cost_by_town %>% filter(Cum_Perc <= 80))
```

**Plots of the top 10 Towns which correspond 80% of the DEMAND, RETURN (UNITS) and COST WITH RETURN**
**It's been shown only the top 10 because of the legibility of the plots**

DEMAND
```{r}
ggplot(demand_by_town[1:10, ] %>% filter(Cum_Perc <= 80),
       aes(x = reorder(Town, -Demanda_uni_equil), y = Demanda_uni_equil)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('DEMAND BY TOWN (10+)') +
  xlab('TOWNS') +
  ylab('DEMAND IN UNITS') +
  ylim(0, max(demand_by_town$Demanda_uni_equil) * 1.05) +
  labs(subtitle = paste(
    round(nrow(demand_by_town %>% filter(Cum_Perc <= 80)) / nrow(demand_by_town) * 100, 2),
    "% of the ",
    nrow(demand_by_town),
    " Towns represent ",
    max(demand_by_town %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the Demand", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(demand_by_town[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 10.63% of the total of demand*

RETURNED UNITS
```{r}
ggplot(return_by_town[1:10, ] %>% filter(Cum_Perc <= 80),
       aes(x = reorder(Town, -Dev_uni_proxima), y = Dev_uni_proxima)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('TOWNS WITH THE HIGHEST RETURNED UNITS (10+)') +
  xlab('TOWNS') +
  ylab('RETURNED UNITS') +
  ylim(0, max(return_by_town$Dev_uni_proxima) * 1.05) +
  labs(subtitle = paste(
    round(nrow(return_by_town %>% filter(Cum_Perc <= 80)) / nrow(return_by_town) * 100, 2),
    "% of the ",
    nrow(return_by_town),
    " Towns represent ",
    max(return_by_town %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the returned units", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(return_by_town[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 43.13% of the total of the returned units*

COST OF RETURN
```{r}
ggplot(cost_by_town[1:10, ] %>% filter(Cum_Perc <= 80),
       aes(x = reorder(Town, -Dev_proxima), y = Dev_proxima)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('TOWNS WITH THE HIGHEST COSTS OF RETURNS (10+)') +
  xlab('TOWNS') +
  ylab('RETURN IN PESOS') +
  ylim(0, max(cost_by_town$Dev_proxima) * 1.05) +
  labs(subtitle = paste(
    round(nrow(cost_by_town %>% filter(Cum_Perc <= 80)) / nrow(cost_by_town) * 100, 2),
    "% of the ",
    nrow(cost_by_town),
    " Town represent ",
    max(cost_by_town %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the Costs of the Returns", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(cost_by_town[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 13.48% of the total of the costs with return*

**As the first sub selection, it' being considered only the 80% of the returned units from the list_products**
List of towns which represent about 80% of the returns of the list_products
```{r}
list_towns <- as.vector(unlist(return_by_town %>% filter(Cum_Perc <= 80) %>% select(Town)))
```

## Clients Analysis using the list of towns which represent 80% of the total of returned units of the 
```{r}
clients_analysis <- train_set %>% filter(Product %in% list_products & Town %in% list_towns) %>% select(NombreCliente, Venta_uni_hoy, Venta_hoy, Dev_uni_proxima, Dev_proxima, Demanda_uni_equil)
clients_analysis <- distinct(clients_analysis %>%
                             group_by(NombreCliente) %>%
                             mutate(
                               Venta_uni_hoy = sum(Venta_uni_hoy),
                               Venta_hoy = sum(Venta_hoy),
                               Dev_uni_proxima = sum(Dev_uni_proxima),
                               Dev_proxima = sum(Dev_proxima),
                               Demanda_uni_equil = sum(Demanda_uni_equil)
                             ), NombreCliente, .keep_all = T)
```

Checking the number of locations
```{r}
length(unique(clients_analysis$NombreCliente))
```

**Since the number of clients is too high, it will be calculated only the clients which represent 80% of returns of the list_towns, keeping the same approach**

Return by product
```{r}
demand_by_client <- data.frame(clients_analysis[order(-clients_analysis$Demanda_uni_equil),][,c(1, 6)])
demand_by_client <- demand_by_client %>% mutate(
  Cum_Dev = cumsum(Demanda_uni_equil),
  Perc = round((Demanda_uni_equil / sum(Demanda_uni_equil)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Demanda_uni_equil)) * 100 , 2)
)
```

Table of the clients which correspond 80% of the total of the demand of the list_towns
```{r, results='asis'}
kable(head(demand_by_client %>% filter(Cum_Perc <= 80), 50), caption = '50 first results')
return_by_client <- data.frame(clients_analysis[order(-clients_analysis$Dev_uni_proxima),][,c(1, 4)])
return_by_client <- return_by_client %>% mutate(
  Cum_Dev = cumsum(Dev_uni_proxima),
  Perc = round((Dev_uni_proxima / sum(Dev_uni_proxima)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Dev_uni_proxima)) * 100 , 2)
)
```

Table of the clients which correspond 80% of the total of returned units of the list_towns
```{r, results='asis'}
kable(head(return_by_town %>% filter(Cum_Perc <= 80), 50), caption = '50 first results')
cost_by_client <- data.frame(clients_analysis[order(-clients_analysis$Dev_proxima),][,c(1, 5)])
cost_by_client <- cost_by_client %>% mutate(
  Cum_Dev = cumsum(Dev_proxima),
  Perc = round((Dev_proxima / sum(Dev_proxima)) * 100 , 2),
  Cum_Perc = round((Cum_Dev / sum(Dev_proxima)) * 100 , 2)
)
```

Table of the clients which correspond 80% of the total of the costs with returns of the list_towns
```{r, results='asis'}
kable(head(cost_by_town %>% filter(Cum_Perc <= 80), 50), caption = '50 first results')
```

**Plots of the top 10 Clients which correspond 80% of the DEMAND, RETURN (UNITS) and COST WITH RETURN**
**It's been shown only the top 10 because of the legibility of the plots**

DEMAND
```{r}
ggplot(demand_by_client[1:10, ],
       aes(x = reorder(NombreCliente, -Demanda_uni_equil), y = Demanda_uni_equil)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('DEMAND BY CLIENTS (10+)') +
  xlab('CLIENTS') +
  ylab('DEMAND IN UNITS') +
  ylim(0, max(demand_by_client$Demanda_uni_equil) * 1.05) +
  labs(subtitle = paste(
    round(nrow(demand_by_client %>% filter(Cum_Perc <= 80)) / nrow(demand_by_client) * 100, 2),
    "% of the ",
    nrow(demand_by_client),
    " Clients represent ",
    max(demand_by_client %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the Demand", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(demand_by_client[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 19.85% of the total of demand*

RETURNED UNITS
```{r}
ggplot(return_by_client[1:10, ] %>% filter(Cum_Perc <= 80),
       aes(x = reorder(NombreCliente, -Dev_uni_proxima), y = Dev_uni_proxima)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('CLIENTS WITH THE HIGHEST RETURNED UNITS (10+)') +
  xlab('CLIENTS') +
  ylab('RETURNED UNITS') +
  ylim(0, max(return_by_client$Dev_uni_proxima) * 1.05) +
  labs(subtitle = paste(
    round(nrow(return_by_client %>% filter(Cum_Perc <= 80)) / nrow(return_by_client) * 100, 2),
    "% of the ",
    nrow(return_by_client),
    " Clients represent ",
    max(return_by_client %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the returned units", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(return_by_client[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 58.55% of the total of the returned units*

COST OF RETURN
```{r}
ggplot(cost_by_client[1:10, ] %>% filter(Cum_Perc <= 80),
       aes(x = reorder(NombreCliente, -Dev_proxima), y = Dev_proxima)) +
  geom_col(fill = 'lightblue', color = 'darkblue', alpha = 0.7) +
  geom_text(aes(label = paste(Perc, '%', sep = '')), vjust = -0.5, size = 3) +
  ggtitle('CLIENTS WITH THE HIGHEST COSTS OF RETURNS (10+)') +
  xlab('CLIENTS') +
  ylab('RETURN IN PESOS') +
  ylim(0, max(cost_by_client$Dev_proxima) * 1.05) +
  labs(subtitle = paste(
    round(nrow(cost_by_client %>% filter(Cum_Perc <= 80)) / nrow(cost_by_client) * 100, 2),
    "% of the ",
    nrow(cost_by_client),
    " Clients represent ",
    max(cost_by_client %>% filter(Cum_Perc <= 80) %>% select(Cum_Perc)),
    "% of the Costs of the Returns", sep = '')) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.5, face = 'bold'),
        axis.text.x = element_text(angle = 90, hjust = 1),
        plot.subtitle = element_text(hjust = 0.5, vjust = 0.5))
paste(cost_by_client[10, 'Cum_Perc'], '%', sep='')
```
*The top 10 represent 24.07% of the total of the costs with return*

List of clients
```{r}
list_clients <- as.vector(unlist(return_by_client %>% filter(Cum_Perc <= 80) %>% select(NombreCliente)))
```

## Functions to calculate the demand

Before define the method that will be used to predict the demand, it was suggested to test if the data set is able to be handle by a linear regression.
To be able, it's important that there are multiple occurrences of combined variables (Product, Town, NombreCliente) to train the model and then make the predictions.
To guarantee a fast and efficient return, it will be considered the lists of products, town and client, compiled throughout previous analysis:<br />
**list_products:** list of products which represent 80% of the total of returned units<br />
**list_towns:** list of towns which represent 80% of the total of returned units from the list_products<br />
**list_clients:** list of towns which represent 80% of the total of returned units from the list_towns<br />

Filtering the demands by List_products, List_towns and List_clients
```{r}
train_set_result <- train_set %>% filter(Product %in% list_products & Town %in% list_towns & NombreCliente %in% list_clients)
```

Checking the occurrences of combined variables
```{r}
combined_variables <- table(data.frame(train_set_result %>% mutate(features = paste(Product, Town, NombreCliente)))[, 'features'])
combined_variables <- data.frame(combined_variables)
colnames(combined_variables) <- c('Variables', 'Frequency')
sum(combined_variables %>% filter(Frequency == 1) %>% select(Frequency))
```
**Since the number of unique occurrences are too high, it's being considered not appropriate to address the dataset through a linear regression**

With this approach it's being analyzed about 51.06% of the total of returns
```{r, results='asis'}
paste(round((sum(train_set_result$Dev_uni_proxima) / sum(train_set$Dev_uni_proxima)) * 100, 2), '%', sep='')
train_set_result <- train_set_result[, c(2, 4, 6, 7, 10:14)]
kable(head(train_set_result))
```

**Since the Dev_uni_proxima has to do to the returned units per week, it's important to focus on the Town and Client. So it's recommended to reduce the mean of returns calculated by week as in the function**

This function returns the combination of Product, Town and Client per week, ordered by the most returned products from set which most impacts in about 51% of the returns.

By this function, it's possible to adjust the combined variables with efficiency
```{r, results='asis'}
suggested_demand <- function(){
  result <- distinct(train_set_result %>%
                       group_by(Product, Town, NombreCliente) %>%
                       mutate(
                         Return_mean = mean(Dev_uni_proxima),
                         Demand_min = min(Demanda_uni_equil),
                         Demand_max = max(Demanda_uni_equil),
                         Demand_mean = mean(Demanda_uni_equil)
                       ), Town, NombreCliente, .keep_all = T)
  result <- result[, c(1:3, 10:13)]
  kable(head(result[order(-result$Return_mean), ], 50))
}
suggested_demand()
```

This function lists the combination of Town and Client per week, ordered by the highest number of returns of the Product which was choosed by the user.
```{r, results='asis'}
return_demand_product <- function(prod){
  result <- train_set %>% filter(Product == prod)
  result_2 <- distinct(result %>%
                         group_by(Town, NombreCliente) %>%
                         mutate(
                           Return_mean = mean(Dev_uni_proxima),
                           Demand_min = min(Demanda_uni_equil),
                           Demand_max = max(Demanda_uni_equil),
                           Demand_mean = mean(Demanda_uni_equil)
                         ), Town, NombreCliente, .keep_all = T)
  result_2 <- result_2[, c(2, 4, 6, 15:18)]
  kable(head(result_2[order(-result_2$Return_mean), ], 50))
}
```

**Example of use for the 2nd more returned product**
```{r}
return_demand_product('Nito BIM 62g 1p')
```

---

## Final notes
It's been presented variables which can be used to ponder the demand:<br />
**Demand_min:** minimum of demand per week<br />
**Demand_max:** maximum of demand per week<br />
**Demand_mean:** mean of demand per week<br />

With these numbers, it can be limit the maximum number of products of a specific variable combination, and ponder if the orders are reasonable.
With new datas, this script can be run again and as the returns descrease, new combined features will be shown.